Combined Analysis of All 3 Experiments

### 2023-10-12 Analysis/full_analysis.qmd
create combined doc
add manuscripts

---
title: "Combined Analysis of All 3 Experiments"
categories: [Analysis, R, Bayesian]
---

@@

>>>>

---
title: "Combined Analysis of All 3 Experiments"
categories: [Analysis, R, Bayesian]
execute: 
  warning: false
  eval: false 
---

@@

```{r}
dAll <- readRDS(here("data/dAll_08-21-23.rds"))

f <- (`Band` = vb)* expMode2 ~ dist * Exp* condit * ((`Avg.` = Mean)*Arguments(fmt='%.0f') )

datasummary(f,
            data = dAll,
            output = 'gt',
            sparse_header = TRUE)
